---
output: rmarkdown::github_document
---

# osqueryr

'osquery' 'DBI' and 'dbplyr' Interface for R

## WIP WIP WIP

Not everything works.

NOTE: You need to install `osquery` for this to work. 

Read <https://osquery.readthedocs.io/en/stable/> before proceeding.

## Description

'osquery' <https://osquery.readthedocs.io/en/stable/> is an operating 
system instrumentation framework for 'Windows', 'OS X (macOS)', 'Linux', and 
'FreeBSD'. The tools make low-level operating system analytics and monitoring 
both performant and intuitive. A full 'dbplyr'-compliant 'DBI'-driver 
interface is provided facilitating intuitive and tidy analytic idioms.
  
## What's Inside The Tin

The following functions are implemented:

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/osqueryr")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(osqueryr)
library(tidyverse)

# current verison
packageVersion("osqueryr")

```

```{r}
osqdb <- src_dbi(osqueryr::dbConnect(Osquery()))

osqdb

tbl(osqdb, "dns_resolvers")

glimpse(tbl(osqdb, "osquery_info"))

tbl(osqdb, "processes") %>% 
  filter(name %like% '%fire%') %>% 
  glimpse()
```